---
title: 'final data assignment'
author: "caroline wishner"
date: "9/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
caroline.dataset <- read.csv("caroline-dataset-1.csv")
```

## Introduction
  
## Specific Aims
1. Utilize the data in order to find some correlation between the variables" 

2. Identify and validate the most relevant prediction tool(s) for predicting the risk of developing Hypertension"
  
## Data Representation/Descriptive Stats
"The dataset has the following variables and this is what they mean:

id: Person Identifier

age: Age of the subject

gender: Gender of the subject

height: Height in centimeters

weight: Weight in kilograms

bmi: The calculated body mass index

systolic: Systolic BP at the time of measurement

diastolic: Diastolic BP at the time of measurement
  
```{r}
summary(caroline.dataset)
```

  
  Write up of descriptive statistics of the major variables with a  models relating BMI with systolic BP and a model relating BMI with diastolic BP."
  
```{r}
plot(caroline.dataset$bmi, caroline.dataset$systolic)
```
```{r}
plot(caroline.dataset$bmi, caroline.dataset$diastolic)
```

  